Mood increases during video game play: A naturalistic observational case study of PowerWash Simulator

### 2023-09-11 ms.qmd
fix subset bug
avoid trying to sample when there's not enough data

typo

# Plot: Example raw sessions
set.seed(99)
dat_example_sessions <- dat |>
  add_count(pid, session, name = "obs_per_session") |>
  filter(obs_per_session >= 4) |>
  mutate(session = as.numeric(as.factor(session)), .by = pid) |>
  mutate(session_per_person = length(unique(session)), .by = pid) |>
  filter(session_per_person >= 4) |>
  arrange(pid, session) |>
  filter(pid %in% sample(unique(pid), 3)) |>
  mutate(Session = str_glue("Session {session}"), Person = str_glue("Person {fct_anon(pid)}"))

>>>>

# Plot: Example raw sessions
set.seed(99)
dat_example_sessions <- dat |>
  add_count(pid, session, name = "obs_per_session") |>
  filter(obs_per_session >= 4) |>
  mutate(session = as.numeric(as.factor(session)), .by = pid) |>
  mutate(session_per_person = length(unique(session)), .by = pid)
# default 
min_sessions <- 4 
n_filtered <- dat_example_sessions |> 
  distinct(pid, session_per_person) |> 
  filter(session_per_person >= 4) |> 
  nrow()
# pick anyone if there's not 3 pids with >= 4 sessions
if(n_filtered < 3) min_sessions <- 0
dat_example_sessions <- dat_example_sessions |>
 filter(session_per_person >= min_sessions) |>
  arrange(pid, session) |>
  filter(pid %in% sample(unique(pid), 3)) |>
  mutate(Session = str_glue("Session {session}"), Person = str_glue("Person {fct_anon(pid)}"))
